Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-08 results.tex
Fixed typo
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@967 ccdd05d5-56c1-461a-bf98-85f6876523b4
Small tweaks to figure 3
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@970 ccdd05d5-56c1-461a-bf98-85f6876523b4

We examine the performance of the \lloid\ algorithm on a small region of
compact binary parameter space centered on typical \textsc{ns}--\textsc{ns}
masses.  We begin by constructing a template bank that spans component masses
between 1~and~3~$M_\odot$ using a simulated Advanced \LIGO{} noise
curve~\cite{lal}.  Then we create sub-banks by partitioning the parameter space by
chirp mass.  Figure \ref{fig:tmpltbank} illustrates this procedure.
\begin{figure}[htbp]
	\begin{center}
		\includegraphics{figures/tmpltbank.png}
		\caption{\label{fig:tmpltbank}Placement of template parameters used in this paper.  The template bank consists of 98544 templates with component masses $m_1$, $m_2$, between 1~and~3~$M_\odot$.  We design a filter bank to search for a small subset of these templates with chirp masses $\mathcal M$ between 1.1955~and~1.2045~$M_\odot$.}
	\end{center}
\end{figure}
The result is that we obtain 657 templates with chirp masses between 1.1955~and~1.2045~$M_\odot$.  With this
sub-bank we were able to construct an efficient time-slice decomposition that consisted of 11 time slices
with sample rates between 32 and 4096 Hz shown in table \ref{tab:time_slices}.
\begin{table}
\begin{indented}
\caption{\label{tab:time_slices} Filter design for these 657 templates.  From left to right, this table shows the sample rate, time interval, number of samples, and number of orthogonal templates for each time slice.  We vary \SVD{} tolerance from $\left(1-10^{-1}\right)$ to $\left(1-10^{-6}\right)$.}
\item[]\begin{tabular}{rr@{,\,}lc*{6}{r}}
\br
\multicolumn{4}{c}{} &\centre{6}{$\log_{10}$ (1$-$\SVD{} tolerance)} \\
\ns
\multicolumn{4}{c}{} &\crule{6} \\
$f^s$ (Hz) & $[t^s$&$t^{s+1})$ (s) & $N^s$ & $-1$ & $-2$ & $-3$ & $-4$ & $-5$ & $-6$ \\
\mr
4096 & [0&0.5) & 2048 & 1 & 4 & 6 & 8 & 10 & 14 \\
512 & [0.5&4.5) & 2048 & 2 & 6 & 8 & 10 & 12 & 16 \\
256 & [4.5&12.5) & 2048 & 2 & 6 & 8 & 10 & 12 & 15 \\
128 & [12.5&76.5) & 8192 & 6 & 20 & 25 & 28 & 30 & 32 \\
64 & [76.5&140.5) & 4096 & 1 & 8 & 15 & 18 & 20 & 22 \\
64 & [140.5&268.5) & 8192 & 1 & 7 & 21 & 25 & 28 & 30 \\
64 & [268.5&396.5) & 8192 & 1 & 1 & 15 & 20 & 23 & 25 \\
32 & [396.5&460.5) & 2048 & 1 & 1 & 3 & 9 & 12 & 14 \\
32 & [460.5&588.5) & 4096 & 1 & 1 & 7 & 16 & 18 & 21 \\
32 & [588.5&844.5) & 8192 & 1 & 1 & 8 & 26 & 30 & 33 \\
32 & [844.5&1100.5) & 8192 & 1 & 1 & 1 & 12 & 20 & 23 \\
\br
\end{tabular}
\end{indented}
\end{table}
We use this template bank and decomposition for the remainder of this section.

@@

Table~\ref{table:flops} shows that the \lloid\ method requires $\sim 10^8$
\flops\ to cover a sub-bank comprising of $\sim 10^2$ out of the total $\sim
10^5$ mass pairs.  Given that modern (ca. 2011) workstations can sustain
computation rates up to $\sim 10^{10}$ \flops{}, and assuming that other
regions of the parameter space have similar computational scaling\footnote{The
lengths of templates varies over the parameter space; lower-mass templates are
longer and would require more computation to analyze while higher-mass
templates are shorter and would require less. However, we consider the
estimates based on this sub-bank to be a reasonable representation.}, an entire
search could be implemented with $\gtrsim 10$ machines.

>>>>

We examine the performance of the \lloid\ algorithm on a small region of
compact binary parameter space centered on typical \textsc{ns}--\textsc{ns}
masses.  We begin by constructing a template bank that spans component masses
between 1~and~3~$M_\odot$ using a simulated Advanced \LIGO{} noise
curve~\cite{lal}.  Then we create sub-banks by partitioning the parameter space by
chirp mass.  Figure \ref{fig:tmpltbank} illustrates this procedure.
\begin{figure}[htbp]
	\begin{center}
		\includegraphics{figures/tmpltbank.png}
		\caption{\label{fig:tmpltbank}Placement of template parameters used in this paper.  The template bank consists of 98544 templates with component masses $m_1$, $m_2$, between 1~and~3~$M_\odot$.  We design a filter bank to search for a subset of 657 of these templates with chirp masses $\mathcal M$ between 1.1955~and~1.2045~$M_\odot$.}
	\end{center}
\end{figure}
The result is that we obtain 657 templates with chirp masses between 1.1955~and~1.2045~$M_\odot$.  With this
sub-bank we were able to construct an efficient time-slice decomposition that consisted of 11 time slices
with sample rates between 32 and 4096 Hz shown in table \ref{tab:time_slices}.
\begin{table}
\begin{indented}
\caption{\label{tab:time_slices} Filter design for these 657 templates.  From left to right, this table shows the sample rate, time interval, number of samples, and number of orthogonal templates for each time slice.  We vary \SVD{} tolerance from $\left(1-10^{-1}\right)$ to $\left(1-10^{-6}\right)$.}
\item[]\begin{tabular}{rr@{,\,}lc*{6}{r}}
\br
\multicolumn{4}{c}{} &\centre{6}{$\log_{10}$ (1$-$\SVD{} tolerance)} \\
\ns
\multicolumn{4}{c}{} &\crule{6} \\
$f^s$ (Hz) & $[t^s$&$t^{s+1})$ (s) & $N^s$ & $-1$ & $-2$ & $-3$ & $-4$ & $-5$ & $-6$ \\
\mr
4096 & [0&0.5) & 2048 & 1 & 4 & 6 & 8 & 10 & 14 \\
512 & [0.5&4.5) & 2048 & 2 & 6 & 8 & 10 & 12 & 16 \\
256 & [4.5&12.5) & 2048 & 2 & 6 & 8 & 10 & 12 & 15 \\
128 & [12.5&76.5) & 8192 & 6 & 20 & 25 & 28 & 30 & 32 \\
64 & [76.5&140.5) & 4096 & 1 & 8 & 15 & 18 & 20 & 22 \\
64 & [140.5&268.5) & 8192 & 1 & 7 & 21 & 25 & 28 & 30 \\
64 & [268.5&396.5) & 8192 & 1 & 1 & 15 & 20 & 23 & 25 \\
32 & [396.5&460.5) & 2048 & 1 & 1 & 3 & 9 & 12 & 14 \\
32 & [460.5&588.5) & 4096 & 1 & 1 & 7 & 16 & 18 & 21 \\
32 & [588.5&844.5) & 8192 & 1 & 1 & 8 & 26 & 30 & 33 \\
32 & [844.5&1100.5) & 8192 & 1 & 1 & 1 & 12 & 20 & 23 \\
\br
\end{tabular}
\end{indented}
\end{table}
We use this template bank and decomposition for the remainder of this section.

@@

Table~\ref{table:flops} shows that the \lloid\ method requires $\sim 10^8$
\flops\ to cover a sub-bank comprising $\sim 10^2$ out of the total $\sim
10^5$ mass pairs.  Given that modern (ca. 2011) workstations can sustain
computation rates up to $\sim 10^{10}$ \flops{}, and assuming that other
regions of the parameter space have similar computational scaling\footnote{The
lengths of templates varies over the parameter space; lower-mass templates are
longer and would require more computation to analyze while higher-mass
templates are shorter and would require less. However, we consider the
estimates based on this sub-bank to be a reasonable representation.}, an entire
search could be implemented with $\gtrsim 10$ machines.
